\huge Modeling Intervention Strategies for United States TB Control

### 2013-07-28 in_progress/presentations/poster/reuMHC2013.tex

              \caption{Incidence/million for R and NetLogo models (12 runs, $\Delta t$ = 0.1, popConst = 100)}

@@

              \caption{Incidence/million for R and C++ models (2100 runs, $\Delta t$ = 0.01, popConst = 1)}

@@

      \begin{block}{Stochastic Models as a Measure of Variability}
        The stochastic model provides data on the variability of the results
        of the deterministic model.
        \begin{block}{}
          \begin{column}{.45\textwidth}
            \begin{figure}[h]
              \begin{center}
                \includegraphics[width=\textwidth]{IN0dist}
              \end{center}
              \caption{Distribution of USB Incidence (C++) with fitted Normal curve}
              \label{fig:IN0dist}
            \end{figure}
          \end{column}
          \begin{column}{.45\textwidth}
            \begin{figure}[h]
              \begin{center}
                \includegraphics[width=\textwidth]{IN1dist}
              \end{center}
              \caption{Distribution of FB Incidence (C++) with fitted Normal curve}
              \label{fig:IN1dist}
            \end{figure}
          \end{column}
        \end{block}
      \end{block}

>>>>

              \caption{Incidence/million for \texttt{R} and NetLogo models (12 runs, $\Delta t$ = 0.1, popConst = 100)}

@@

              \caption{Incidence/million for \texttt{R} and \texttt{c++} models (2100 runs, $\Delta t$ = 0.01, popConst = 1)}

@@

      \begin{block}{Stochastic Models as a Measure of Variability}
        The stochastic model provides data on the variability of the results
        of the deterministic model.
        \begin{block}{}
          \vspace{-2em}
          \begin{column}{.45\textwidth}
            \begin{figure}[h]
              \begin{center}
                \includegraphics[width=\textwidth]{IN0dist}
              \end{center}
              \caption{USB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 0.233196, \sigma = 0.016534$)}
              \label{fig:IN0dist}
            \end{figure}
          \end{column}
          \begin{column}{.45\textwidth}
            \begin{figure}[h]
              \begin{center}
                \includegraphics[width=\textwidth]{IN1dist}
              \end{center}
              \caption{FB Incidence (\texttt{c++}) with fitted Normal curve ($\mu = 98.6087, \sigma = 0.525294$)}
              \label{fig:IN1dist}
            \end{figure}
          \end{column}
        \end{block}
      \end{block}
